\begin{rubric}{Extracurriculum Activities}
\entry*[2023 -- 2024]%
	\textbf{Collaborator in Communication Department}, Club of Actuary Pioneers, National Economics University.
	\begin{itemize}
		\item Developed high-impact promotional assets to drive attendance and enhance club visibility. 
	\end{itemize}
%
% Blank lines result in extra space!
\entry*[2024]%
	\textbf{Contestant}, MOS World Championship 2024, National Economics University.
	\begin{itemize}
		\item Competed at the regional level in the Microsoft PowerPoint 365 track.
		\item Mastered complex slide master workflows, multimedia integration, and sophisticated animation techniques under competitive constraints.
	\end{itemize}
%

%
\entry*[2024 -- 2026]%
	\textbf{Member of Communication Department}, Union of Faculty of Mathematical Economics, National Economics University. 
	\begin{itemize}
		\item Conceptualized and executed visual branding for high-profile charity initiatives and freshman orientation events.
	\end{itemize}
%

\entry*[2025 -- Present]%
	\textbf{Research Assistant}, Predictive Models and Machine Learning Research Applications, National Economics University.
	\begin{itemize}
		\item Actively participated in research projects, including data collection, analysis, and model development.
		\item Developed and implemented AI applications for businesses and organizations.
		\item Engaged and presented multiple technical webinars and workshops to share knowledge and insights with the community.
	\end{itemize}
%
\end{rubric}