\begin{rubric}{Projects}
    \entry*[2025 -- Present]%
    \href{https://rangdong.com.vn/}{\textbf{Rang Dong Sales Agent}}, Rang Dong, Hanoi.
    \begin{itemize}
        \item Engineered a conversational agent that replicates the e-commerce web navigation experience, guiding customers through product discovery and purchase decision funnels via natural language.
        \item Enhanced user engagement by providing an intuitive alternative to traditional site navigation.
    \end{itemize}
    %
    \entry*[December, 2025]%
    \textbf{Gigabyte Sales Agent}, Hackathon \href{https://www.facebook.com/profile.php?id=61576714508472}{``Master AI, Master Careers''}, Ho Chi Minh City.
    \begin{itemize}
        \item Addressed the high-friction nature of purchasing laptops and monitors by automating answers to technical queries, streamlining the pre-sales support process.
        \item Awarded 1st place in the hackathon.
    \end{itemize}
    %
    \entry*[November, 2025]%
    \href{https://github.com/tlong-ds/hanoi-weather-forecast}{\textbf{Hanoi Weather Forecast}}, Group Project, National Economics University, Hanoi.
    \begin{itemize}
        \item Developed a weather forecasting model for Hanoi using machine learning frameworks like Scikit-learn, ClearML and Catboost.
        \item Designed a dashboard to visualize the weather data and the model performance.
    \end{itemize}
    % 
    \entry*[June, 2025]%
    \href{https://github.com/tlong-ds/thelearninghouse}{\textbf{The Learning House}}, Group Project, National Economics University, Hanoi.
    \begin{itemize}
        \item Fully functional educational platform with rich AI features for learners.
        \item Created a dashboard to visualize the learners' progress.
        \item Utilized Amazon S3 for storing medias.
    \end{itemize}
\end{rubric}

