\begin{rubric}{Research Experience}
    \entry*[2025 -- Present]%
    \textbf{Research Assistant}, Predictive Models and Machine Learning Research Applications, NEU.
    \begin{itemize}
        \item Contributed to multiple industry-linked projects, bridging academic research with business applications via predictive modeling.
        \item Fine-tuned transformer-based architectures (BERT/RoBERTa) for domain-specific NLP tasks.
        \item Hosted local seminars and technical training sessions for lab members, fostering a collaborative research environment and knowledge sharing.
        \item In preparation of the publication: \textit{``Agentic B2B2C AI - how AI has been transforming B2B2C E-commerce in Vietnam''}.
    \end{itemize}
%
\entry*[2024 -- 2025]%
    \textbf{Student Researcher}, Scientific Student Research Competition, NEU.
    \begin{itemize}
        \item Co-authored the paper \textit{``The Regulatory Role of Provincial Governments in the Impact of Labor Shift on Agricultural Production Efficiency in Vietnam''}, published in \textit{Proceedings of the National Scientific Conference: Vietnam's Economy in 2024 and Prospects for 2025}, pp. 488--501.
        \item Implemented \textbf{spatial econometric models with panel data} to quantify policy impact, utilizing rigorous statistical tests to validate hypothesis significance.
        \item Recognized with the university-level \textbf{``Student Research Award 2026''} for methodological excellence.
    \end{itemize}
\end{rubric}
